---
title: "Booking Apps Data Scraping"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    number_sections: true
    theme: united
    highlight: espresso
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  class.output = ".scroll-500",
  comment = "#>"
)
options(scipen = 9999)
options(warn = -1) # remove warning messages
```

# __Library Setup__

```{r}
library(tidyverse)
library(rvest)
library(stringr)
library(rlist)
```

# __Booking Apps Data Scraping__

Read the HTML code from the Google Play Store website - Travel Apps

```{r}
# URL of Google Play Store - Apps- Travel
url <- "https://play.google.com/store/search?q=travel&c=apps"

# Reading the HTML code from the website
web <- read_html(url)
```

Scrape the application's names

```{r}
# Specifying class of the application's names
names_html <- html_nodes(web,'.WsMG1c.nnK0zc')

# Converting the application's names data to text
names_data <- html_text(names_html)
```

Scrape the application's ratings

```{r}
# Specifying class of the application's ratings
ratings_html <- html_nodes(web, '.pf5lIe') %>% html_children() 

# Extract the ratings from the image label
ratings <- html_attr(ratings_html,'aria-label')
ratings_data <- word(sub('.*Rated', '', ratings), 2)

# Convert ratings to numeric data
ratings_data <- as.numeric(ratings_data)
```

Scrape the application's links

```{r}
# Specifying class of the application's ratings
link_html <- html_nodes(web, '.wXUyZd') %>% html_children() 

# Extract the ratings from the image label
link_data <- html_attr(link_html,'href')
```

Combine all scraping results to one dataframe

```{r}
# Combine all scraping result to bookapp dataframe
bookapp <- data.frame(
  "Application_Name" = names_data,
  "Ratings" = ratings_data,
  "Install_Link" = paste0("https://play.google.com",link_data)
)

# Only take Traveloka, Tiket.com, Pegipegi, Tripadvisor, Booking.com, Agoda data
travel <- c("Traveloka: Book Hotel, Flight Ticket & Activities","tiket.com - Hotels, Flights, To Dos",
            "Booking.com: Hotels, Apartments & Accommodation", "Tripadvisor Hotel, Flight & Restaurant Bookings", "Pegipegi - Buy Hotel, Flight, Train & Bus Ticket", "Agoda")
book_app <- bookapp[bookapp$Application_Name %in% travel,]
```

Scrape the application's logo

```{r, results= 'hide'}
# Initiate logo file names list
logo_data<- list()

# Download all the logo 
for(i in 1:6){
  # Specifying link to the logo page
  logo_link <- book_app$Install_Link[i]
  # Reading the HTML Code
  logo_page <- read_html(logo_link)
  # Specifying logo class
  logo_html <- html_nodes(logo_page, '.xSyT2c') %>% html_children()
  # Take logo link
  logo_src <- html_attr(logo_html, 'src')
  # Name for the logo file
  name <- word(book_app$Application_Name[i],1)
  name <- gsub("[[:punct:]]", "", name)
  # Combine logo name in one list
  logo_data <- c(logo_data, name)
  # Download the logo
  download.file(logo_src, paste0("Logo/",name,".jpg"), mode='wb')
}

# Add logo path to the book_app dataframe
book_app <- book_app %>%  
  mutate("Logo_Path" = paste0("Logo/", logo_data, ".jpg"))
```

Overview of the Data

```{r, echo=FALSE}
book_app
```


# __Booking App's Profile Data Scraping__

Create list for profile data

```{r}
profile_data <- list()
```

Scrape Traveloka's profile

```{r}
# Reading HTML Code from the website
traveloka_web <- read_html("https://www.traveloka.com/en-id/about-us")

# Specifying class of the profile
traveloka_html <- html_node(traveloka_web,'.mcp-placeholder-inner') %>% html_children()

# Converting the application's names data to text
traveloka_data <- html_text(traveloka_html)
traveloka_data <- gsub("\n","",traveloka_data)

# Add traveloka profile to list
profile_data <- c(profile_data, traveloka_data)
```

Scrape Tiket.com's profile

```{r}
# Reading HTML Code from the website
tiket_web <- read_html("https://centreforaviation.com/data/profiles/suppliers/pt-global-tiket-network")

# Specifying class of the profile
tiket_html <- html_node(tiket_web,'.about_bio_WkT') %>%  html_children()

# Converting the application's names data to text
tiket_data <- html_text(tiket_html[2])

# Add traveloka profile to list
profile_data <- c(profile_data, tiket_data)
```

Scrape Booking.com's profile

```{r}
# Reading HTML Code from the website
booking_web <- read_html("https://www.booking.com/content/about.en-gb.html?label=gen173nr-1DCBQoggJCBWFib3V0SAlYBGhoiAEBmAEJuAEIyAEM2AED6AEBiAIBqAIDuALmm7z-BcACAdICJDRkMzA0MjAyLWQyZTctNGFkZS1hYjczLTI5ZDk2MmY0Nzg5ZdgCBOACAQ;sid=66417274f3216deaf8cdde1d344ff462;keep_landing=1&")

# Specifying class of the profile
booking_html <- html_node(booking_web,'.static_highlighted') %>%  html_children()

# Converting the application's names data to text
booking_data <- html_text(booking_html[3])
booking_data <- gsub("\n","", booking_data)

# Add traveloka profile to list
profile_data <- c(profile_data, booking_data)
```

Scrape Tripadvisor's profile

```{r}
# Reading HTML Code from the website
trip_web <- read_html("https://tripadvisor.mediaroom.com/IN-about-us")

# Specifying class of the profile
trip_html <- html_node(trip_web,'.content') %>% html_children() %>% html_children()
trip_html <- trip_html[2] %>% html_children()

# Converting the application's names data to text
trip_data <- html_text(trip_html[1])

# Add traveloka profile to list
profile_data <- c(profile_data, trip_data)
```

Scrape Pegipegi's profile

```{r}
# Reading HTML Code from the website
pegi_web <- read_html("https://www.pegipegi.com/team/")

# Specifying class of the profile
pegi_html <- html_node(pegi_web,'.content01') %>% html_children() 

# Converting the application's names data to text
pegi_data <- html_text(pegi_html[5])

# Add traveloka profile to list
profile_data <- c(profile_data, pegi_data)
```

Scrape Agoda's profile

```{r}
# Reading HTML Code from the website
agoda_web <- read_html("https://my.wobbjobs.com/users/companies/agoda-com")

# Specifying class of the profile
agoda_html <- html_node(agoda_web,'.section') %>%  html_children() %>% html_children()

# Converting the application's names data to text
agoda_data <- html_text(agoda_html[3])
agoda_data <- sub('.*About Agoda ', '', agoda_data)

# Add traveloka profile to list
profile_data <- c(profile_data, agoda_data) 
```

# __Combine All Scraping Results__

Add profile data to the dataframe

```{r}
profile_data <- profile_data %>% unlist()

book_app <- book_app %>% 
  mutate("Profile" = profile_data)
```

Overview of the data

```{r, echo=FALSE}
book_app
```

Save the dataframe to Booking_Apps.csv

```{r}
write.csv(book_app,"Data/Booking_Apps.csv", row.names = FALSE)
```

